results

### 2024-02-19 reproduce-results.qmd
supporting variant strains

This quarto document reproduces the results section in Nascimento de Lima et al. (2024). *The value of environmental surveillance for pandemic response*.

>>>>

This quarto document reproduces the results section in Nascimento de Lima et al. (2024). *The value of environmental surveillance for pandemic response*. For details on how to install dependencies, and reproduce these results, see the `README.md` file.

# Run Results

First, we instantiate the model and run it over the experimental designs used in the paper.

```{r}

```

## Value of EWS under base-case results
{Describe dynamics and results uder base-case assumptions}

D. EWS provide meaningful value under base-case assumptions

## Conditions for high-value early warning 
{Describe conditions under which value is lower or higher}
D. Value of EWS hinges on timeliness of and adherence to NPIs. 
There was a

## EWS and policy coordination
D. EWS alleviate lack of policy coordination. 
There is a concern that EWS data will need to be integrated to be useful. However, we find that policy coordination and EWS act as substitutes. Policy coordination h

## Marginal Value of EWS
D. EWS deployment also face decreasing marginal returns
The value of EWS decreases as coverage increases.
